### 2018-02-11 Writing/draft.tex
comments/edits on beginning of methods

In the example in Table \ref{Tab:example_matrix}, the characters \textbf{C1} and \textbf{C2} are the most likely to be truly independent; characters \textbf{C3} and \textbf{C4} suffer from a a coding induced dependency; characters \textbf{C1} and \textbf{C3}/\textbf{C4} have an evolutionary induce dependency and again, characters \textbf{C2} and \textbf{C3}/\textbf{C4} are likely to be independent.
Yet a phylogenetic software will treat all these four characters in exactly the same way: only the sheer difference between the different character states tokens will be used in order to infer a phylogenetic tree.
It is thus still unclear what will be the effect of characters correlation on phylogenetic inference: how does these correlation really affect topology?

@@

We applied the following simulation protocol to assess the effect of character correlation on the accuracy of tree inference (Fig.\ref{Fig:outline}):
\begin{enumerate}
    \item \textbf{Simulating matrices}: we simulated discrete morphological matrices with 25, 75 and 150 taxa for 100, 350 and 1000 characters, hereafter called the ``normal'' matrices. This step resulted in 9 matrices.
    \item \textbf{Modifying matrices}: we modified the ``normal'' matrices by modified the characters in order to maximise or minimise characters differences (hereafter called respectively ``maximised'' and ``minimised'' matrices) by removing respectively the least or most different characters and replacing them randomly by the remaining characters.
    We also randomly duplicated characters from the ``normal'' matrices without biasing towards maximising or minimising character differences to create randomised matrices (hereafter called the ``randomised'' matrices - equivalent to a null expectancy). This step resulted in 36 matrices.
    \item \textbf{Inferring topologies}: we inferred the topologies from the ``normal'', ``maximised'', ``minimised'' and ``randomised'' matrices using both Maximum Parsimony and Bayesian inference (hereafter called the ``normal'', ``maximised'', ``minimised'' and ``randomised'' trees). This step resulted in 72 topologies.
    \item \textbf{Comparing topologies}: finally, we compared the ``normal'' to the ``maximised'', ``minimised'' and ``randomised'' trees to measure the effect of character correlation on topology.
\end{enumerate}
Each step was replicated 40 times and are described below in more details, along with our proposed definition for measuring the difference between characters.

>>>>

In the example in Table \ref{Tab:example_matrix}, the characters \textbf{C1} and \textbf{C2} are the most likely to be truly independent; characters \textbf{C3} and \textbf{C4} suffer from a a coding induced dependency; characters \textbf{C1} and \textbf{C3}/\textbf{C4} have an evolutionary induce dependency and again, characters \textbf{C2} and \textbf{C3}/\textbf{C4} are likely to be independent.
Yet a phylogenetic software will treat all these four characters in exactly the same way: only the sheer difference between the different character states tokens will be used in order to infer a phylogenetic tree.
% I'm unsure what point this introduction serves. It somehow doesn't quite connect with what you say next. I think we can simply focus on the fact that the phenomenon hasn't been empirically explored. 
% I think the point in this manuscript should be: OK, we believe two reasonable things: some characters will be expected to covary in a non-phylogenetic way, and that this phenomenon can reasonably be expected to mislead phylogenetic analysis. 
% The question then becomes: how bad does it have to be to be a real effect?
% Along with this are subquestions:
% If you've got intrinsic correlations, then those correlations could occur across anatomical systems. Would their effects cancel each other out?
% Will "noisier" characters accurately cancel out the effects of correlation?

It is thus still unclear what will be the effect of character correlation on phylogenetic inference: how does these correlation really affect topology?

@@

To assess the effects of character correlation on the accuracy of phylogenetic inference we generated a series of matrices exhibiting different levels of correlation between some characters (Fig.\ref{Fig:outline}):
\begin{enumerate}
    \item \textbf{Simulating matrices}: we simulated discrete morphological matrices with 25, 75 and 150 taxa for 100, 350 and 1000 characters, hereafter called the ``normal'' matrices. This step resulted in 9 matrices.
% HOW do you simulate them? What models do you use? What protocol? Are the simulated matrices expected to recover the correct topology in the absence of ourmanipulations? 
    \item \textbf{Modifying matrices}: we modified the ``normal'' matrices by modifying the characters in order to maximise or minimise characters differences (hereafter called respectively ``maximised'' and ``minimised'' matrices) by removing respectively the least or most different characters and replacing them randomly by the remaining characters.
% I don't understand this. Would a matrix with a "maximised" level of correlation simply be a uniform matrix?
% What do you mean by "least" and "most different"? What is the measure of similarity? 
% What do you mean "replacing them randomly by the remaining characters? Also: won't that simply create a correlation with another character in the dataset?

    We also randomly duplicated characters from the ``normal'' matrices without biasing towards maximising or minimising character differences to create randomised matrices (hereafter called the ``randomised'' matrices - equivalent to a null expectancy). This step resulted in 36 matrices.

\item \textbf{Inferring topologies}: we inferred the topologies from the ``normal'', ``maximised'', ``minimised'' and ``randomised'' matrices using both maximum parsimony (MP) and Bayesian inference (hereafter called the ``normal'', ``maximised'', ``minimised'' and ``randomised'' trees). This step resulted in 72 topologies.
    \item \textbf{Comparing topologies}: finally, we compared the ``normal'' to the ``maximised'', ``minimised'' and ``randomised'' trees to measure the effect of character correlation on topology.
\end{enumerate}
Each step was replicated 40 times and are described below in more detail, along with our proposed definition for measuring the difference between characters.
